---
title: "Vignette of the a4Reporting package"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float:
      collapsed: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{a4Reporting package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Introduction

This document explains the functionalities available in the
**a4Reporting** package.


This package contains utility functions to enhance reporting of data for the Automated Affymetrix Array Analysis 
suite of packages.

```{r loadLibraries, results = 'hide', echo = FALSE}

	library(a4Reporting)

```

# Create an annotation table

The `annotationTable` function enhances the reporting of table of genes or gene ontology term.

# Top table of classification objects

A few utility functions to enhances the reporting of top tables for
`glmnet`, `lognet`, `elnet`, `pam` and `pam` classification confusion 
are available.

# Appendix

## Session information

```{r sessionInformation, echo = FALSE}
print(sessionInfo())
```